\section{Context}\label{s:context}
As testified in \cite{ZIEGLERGRAHAM2008422} "One in 190 Americans is currently living with the loss of a limb. Unchecked, this number may double by the year 2050": this kind of statistic can easily express how much prosthetic technologies are important nowadays and how big is the market for them.
By virtue of the above-mentioned high demand of prosthesis, technological research in the prosthetic domain in the last decades has been very active: ideally amputees would need, as far as possible, prosthesis as functional as real limbs and a great deal of research as been done to try to enhance the performance, the comfort and the appearance of prosthetic limbs. Sadly, even with all the effort done from the scientific community, we are still far from developing this kind of prosthetic limbs: in particular, even if relatively dexterous prostheses are commercially available, reliable prosthetic control is still an open problem. As testified in \cite{castellini2016upper}, detecting the patient's intent and transforming it into effective control signals is still a largely open problem. During the last few years machine learning has become more and more common as control method: various machine learning model has been used to extrapolate control policy from data provided from disparate type of sensors.
One of the most commonly used sensor is the electromyographic (EMG) sensor, which allows to measure the electrical activity of muscles: this kind of sensor owes its popularity to its (relatively) low cost and to the fact that it can be used without the need of invasive surgical procedures. Although the control methods for prosthesis using EMG signals are constantly improving, from \cite{Zecca2002} to \cite{Strazzulla2017}, the control system is still the bottleneck for the diffusion of machine learned controlled prosthesis in the daily life of the standard amputee: in particular the main problem of the current state of the art machine learned controller is the reliability, e.g. the ever-present possibility that the system will take the wrong decision, potentially leading to catastrophic results.
In the last years the interest in the reliability of machine learning system has increased more and more: in particular for safety critical application it is imperative to guarantee an high reliability and current machine learning systems are usually unable to guarantee it. One of the current state of the art methods used to enhance the reliability of machine learning system consist in leveraging formal methods in order to verify and eventually repair machine learning system. This kind of method has been mainly applied to neural networks system and a thorough presentation of its state of the art can be found in \cite{leofante2018automated}.